\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex
more conclusion

In this work, we show how we can harness photometric data collected by the \TESS mission
to construct a map of Sol d, a rocky planet ‎with a radius of $6.4\times 10^6$~m
orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
star \citep{Sagan1993}. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
the habitable zone for follow-up with other missions, it came as a great surprise
that data from the spacecraft could be used not only to detect Sol d but to
characterize it in detail. This is due primarily to the strong nature of the reflected
light signal originating from the planet, which 
because of complex internal optics illuminates the entirety of the \TESS detector 
during most of Sector 1 and part of Sector 2.

@@

The likely prevalence of continents, oceans, and complex weather patterns 
on Sol d make it an extremely promising site for the evolution of life. 
We strongly advocate for future missions to further investigate this possibility. 
In particular, Sol d may be a good choice of target for a lander mission. 
One prime landing site is located at the planetary (latitude, longitude) coordinates 
($33.3943^\circ$ N, $104.5230^\circ$ W).\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (private communication, Andrew R. Casey) led us to conclude that this would not be a suitable location.}

The work presented here also serves as a relevant case study for future 
efforts to characterize terrestrial exoplanets. \todo{(more)}

>>>>

In this work, we show how we can harness photometric data collected by the \TESS mission
to construct a map of Sol d, a rocky planet âwith a radius of $6.4\times 10^6$~m
orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
star \citep{Sagan1993}. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
the habitable zone for follow-up with other missions, it came as a great surprise
that data from the spacecraft could be used not only to detect Sol d but to
characterize it in detail. This is due primarily to the strong nature of the reflected
light signal originating from the planet, which 
because of complex internal optics illuminates the entirety of the \TESS detector 
during most of Sector 1 and part of Sector 2.

@@

The likely prevalence of continents, oceans, and complex weather patterns 
on Sol d make it an extremely promising site for the evolution of life. 
We strongly advocate for future missions to further investigate this possibility. 
In particular, Sol d may be a good choice of target for a lander mission. 
One prime landing site is located at the planetary (latitude, longitude) coordinates 
($33.3943^\circ$ N, $104.5230^\circ$ W).\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (Andrew R. Casey, personal communication) led us to conclude that this would not be a suitable location.}

The work presented here also serves as a relevant case study for future 
efforts to characterize terrestrial exoplanets. While the circumstances of \TESS's 
observations of Sol d will not be replicated exactly for other planets, similar 
rotationally-modulated phase curves of reflected light may be feasible in the future. 
We show that a fast, analytic linear model can be successfully applied to such data. 
We also underscore the importance of high cadence \emph{and} long duration for 
these observations, and we additionally advocate for multi-wavelength coverage to 
help disentangle the photometric signatures of continents and persistent cloud features.
